EDA

### 2020-02-27 src/draft.Rmd
add tax 2019

---
title: "draft"
author: "Xuechun Lu"
date: "25/02/2020"
output: html_document
---

@@

>>>>

---
title: "EDA"
author: "Xuechun Lu, Yuting Wen"
date: "25/02/2020"
output: html_document
---

@@

2019 tax is missing, we imputed 2019 tax using previous values
```{r}
tax_final <- read.csv("~/Desktop/tax_final.csv")
head(tax_final)

tax_modified <- tax_final  %>% mutate(X2019=tax_final$X2018*(1+(((tax_final$X2017-tax_final$X2016)/tax_final$X2016 + (tax_final$X2018-tax_final$X2017)/tax_final$X2017)/2)))
head(tax_modified)
```
